---
title: "Alcohol vs Seat choice"
author: "Pete Hebert"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# introduction  

$H_0$ There is no difference in the alchohol consumption based on the row you sit in.

$H_a$ There is a difference in the alchohol consumption based on the row you sit in.

# Methods 

The response variable is numerical and the explanatory variable is categorical. Therefore we use numerical~cat.

## results 

### graphical results  

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
 
 
 This boxplot shows that the back row has the most amount of alchohol consumption. The front and middle row has a very little difference between the alchohol they consume. 

  
### get fancy  


```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


## Numerical Summarys 


```{r}
favstats(alcohol~Seat,data=davisdata)
```

This data shows the median of the back row being 4 and it shows that the front has 0 and the middle has a median of 1.

## Inferential Tests

```{r}

```


## Conclusions

Is there a difference between the alcohol consumed between the row you choose to sit in? Yes there is a difference between the alcohol consumed by the row you sit in. Based on the data the people who sit in the back row consume more alcohol. The P value is 0.00016 which is smaller then 0.05 so I will reject the null hypothesis.

